---
title: Interactive plots using R  
author: |
 | Matthew Malishev^1^*
 | _^1^ Department of Biology, Emory University, 1510 Clifton Road NE, Atlanta, GA, USA, 30322_
#bibliography:/Users/malishev/Documents/Melbourne Uni/Thesis_2016/library.bib
fontsize: 10
geometry: margin=1in
documentclass: article
linkcolor: pink
urlcolor: blue
citecolor: red
output:
  pdf_document:
    includes:
      in_header: # add .tex file with header content
    highlight: tango
    template: null
    toc: yes
    toc_depth: 4
    number_sections: false
    fig_width: 4
    fig_height: 5
    fig_caption: true
    df_print: tibble 
    citation_package: biblatex # natbib
    latex_engine: xelatex #pdflatex # lualatex
    keep_tex: true # keep .tex file in dir 
  html_document:
    highlight: tango
    code_folding: hide
    toc: yes
    toc_depth: 4
    number_sections: no
    toc_float: yes
  word_document:
    highlight: tango
    keep_md: yes
    pandoc_args: --smart
    #reference: mystyles.docx
    toc: yes
inludes:
  before_body: before_body.tex
subtitle: 
tags:
- nothing
- nothingness
params: 
  dir: "/Users/malishev/Documents/Melbourne Uni/Programs/R code/rCharts"
  date: !r Sys.Date()
  version: !r getRversion()
  email: "matthew.malishev@gmail.com"
  doi: https://github.com/darwinanddavis/rInteractive
classoption: portrait
# ^['https://github.com/darwinanddavis/rInteractive'] # footnote
vignette: >
  %\VignetteIndexEntry{Useful R code}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

<script type="text/x-mathjax-config">
  MathJax.Hub.Config({ TeX: { equationNumbers: {autoNumber: "all"} } });
</script>

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\  

Date: `r params$date`  
R version: `r params$version`  
*Corresponding author: `r params$email`  
This document can be found at `r params$doi`

\newpage  

## Overview  

Interactive plots using javascript viz, including rCharts, d3js, leaflet, Richshaw, to name a few. `rCharts` uses multiple javascript plotting libraries. Sourced from [http://ramnathv.github.io/rCharts/](http://ramnathv.github.io/rCharts/).  

### Install dependencies
```{r, load packages, include=F, cache=F, message=F, warning=F, results='hide'}
packages <- c("rgdal","dplyr","zoo","RColorBrewer","viridis","plyr","digitize","jpeg","devtools","imager","dplyr","ggplot2","ggridges","ggjoy","ggthemes","svDialogs","data.table","tibble","extrafont","sp")  

if (require(packages)){
    install.packages(packages,dependencies = T)
    require(packages)
}
require(devtools) # get rCharts from github  
install_github('rCharts', 'ramnathv')
lapply(packages,library,character.only=T)

```

### Set plotting function  
```{r eval=F, results="hide"}
require("RCurl")
script <- getURL("https://raw.githubusercontent.com/darwinanddavis/plot_it/master/plot_it.R", ssl.verifypeer = FALSE)
eval(parse(text = script))

cat("plot_it( \n0 for presentation, 1 for manuscript, \nset colour for background, \nset colour palette. use 'display.brewer.all()', \nset alpha for colour transperancy, \nset font style \n)")
plot_it(0,"blue","Spectral","Greens",1,"mono") # set col function params
plot_it_gg("white") # same as above 

```

### `rCharts`  
#### `rCharts` plot functions  
```{r}
types <- c("points","line","bar");types
```

#### Scatterplot      
```{r}
require(rCharts)
## Example 1 Facetted Scatterplot
data <- iris
names(iris) = gsub("\\.", "", names(iris))
r1 <- rPlot(data$SepalLength~data$SepalWidth, data=data, color='Species', type='point')
# r1$show('iframesrc', cdn  = TRUE) # chart shows up on Rpubs but not in Rmd preview 

```

#### Barplot  
```{r, include=T, eval=F} 
# need eval = F to fix 'opts_current' when knitting 
## Example 2 Facetted Barplot
hair_eye = as.data.frame(HairEyeColor)
data <- hair_eye
with(data,rPlot(Freq ~ Hair | Eye, color = 'Eye', data = hair_eye, type = "bar"))
```

### Polychart
[Polychart](https://github.com/Polychart/polychart2)    
```{r, include=T, eval=F} 
# need eval = F to fix 'opts_current' when knitting 
data <- mtcars
r1 <- rPlot(aes(x=region,y=sum(sales)),mpg ~ wt | am + vs, data = data, type = "point", color = "gear")
r1
r1$print("chart1")
```

Adding javascript  
```{javascript}
graph_chart1.addHandler(function(type, e){
  var data = e.evtData;
  if (type === 'click'){
    return alert("You clicked on car with mpg: " + data.mpg.in[0]);
  }
})
```

### MorrisJS  
Interactive time series plot [with Morris JS](https://github.com/oesmith/morris.js)  
```{r, include=T, eval=F} 
# need eval = F to fix 'opts_current' when knitting 
data(economics, package = "ggplot2")
econ <- transform(economics, date = as.character(date))
m1 <- mPlot(x = "date", y = c("psavert", "uempmed"), type = "Line", data = econ)
m1$set(pointSize = 0, lineWidth = 1)
m1
# m1$print("chart2")

```

### NVD3  
Interactive and re-usable charts using d3.js with [NVD3](http://nvd3.org/). Follows work of Mike Bostock with ['Towards re-usable charts'](https://bost.ocks.org/mike/chart/).      

```{r, include=T, eval=F} 
data <- HairEyeColor
data <- subset(as.data.frame(data), Sex == "Male")
n1 <- with(data,nPlot(Freq ~ Hair, group = "Eye", data = data, type = "multiBarChart"))
n1
??nPlot
# n1$print("chart3") 
```

### xCharts  
```{r}

```

### Rickshaw  
Interactive time series with [Rickshaw](http://rpubs.com/Koba/80208). See online example [here](http://timelyportfolio.github.io/rCharts_rickshaw_gettingstarted/) and troubleshooting [here](http://rpubs.com/Koba/80208).     
```{r}
require(slidify)
require(rCharts)

```

Troubleshooting example.  
```{r, include=F, eval=F} 
# need eval = F to fix 'opts_current' when knitting 
#specify the data
data1 = data.frame(
  c( 0, 1, 2, 3 ),
  c( 40, 49, 17, 42 ),
  stringsAsFactors = FALSE
)
colnames(data1) <- c("x","y")
#build the plot
r1 <- Rickshaw$new()
r1$layer(
  y ~ x,
  data = data1,
  type = "area",
  colors= "steelblue",
  height = 240,
  width = 540
)
#turn off all the nice built in features
#to match the sparse first example
r1$set(
  hoverDetail = FALSE,
  xAxis = FALSE,
  yAxis = FALSE,
  shelving = FALSE,
  legend = FALSE,
  slider = FALSE,
  highlight = FALSE
)
r1$show(T) # works locally
r1$save('rickshaw_ts.html', cdn = T) # works as well after launching a local web server
r1$show('iframe', cdn = TRUE) # gives 'opts_current' error
r1$show('iframesrc', cdn  = TRUE) # chart shows up on Rpubs but not in Rmd preview

r1$show('inline', include_assets = TRUE, cdn = TRUE)
r1$print('chart1', include_assets = TRUE, cdn = TRUE)
# both give the following error when attempting to knit:
# pandoc: Could not find data file //cdn.strategiqcommerce.com/ajax/libs/rickshaw/1.2.1/rickshaw.min.css
# Error: pandoc document conversion failed with error 97
# Execution halted
```


### My data examples  
Examples of packages using my own data  
```{r}

```

### Clickme  
Alternative to `rCharts` interactive plotting using [`Clickme`](https://github.com/nachocab/clickme).  

### Other interactive plotting libraries in `R`  
- [Clickme](https://github.com/nachocab/clickme)  
- [Rickshaw](http://rpubs.com/Koba/80208)

### References  
- [Clickme](https://github.com/nachocab/clickme)  
- [NVD3](http://nvd3.org/)  
- [Polychart](https://github.com/Polychart/polychart2)  
- [rCharts](http://ramnathv.github.io/rCharts/)  
- [Introduction to rCharts](http://ramnathv.github.io/rCharts/)     
- [Rickshaw](http://rpubs.com/Koba/80208)  
- xCharts    




